Fail Faster

### 2025-03-19 paper/paper.tex
we love the swarm plot

\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of each task's speedup over case studies and strategies, showing that staging leads to better bug-finding ability across the board. As in \todo{earlier figure}, benchmarks with higher numbers of binds (BST (Single-Pass), STLC) see more benefit from staging, whereas benchmarks with more sampling (BST) see a greater speedup from the CSR \rand.}
  \label{fig:etna}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale=0.355]{hist.png}
  \label{fig:swarm}
  \caption{Histogram of individual-task speedups across different staging strategies and benchmarks. Extreme outliers correspond to large speedups.}
\end{figure}

@@

\section{Related Work}
\jwc{A generator is a parser of randomness, and people have implemented lots of staged parser libraries!}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

>>>>

\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of each task's speedup, showing that staging leads to better bug-finding ability across the board. As in \todo{earlier figure}, benchmarks with higher numbers of binds (BST (Single-Pass), STLC) see more benefit from staging, whereas benchmarks with more sampling (BST) see a greater speedup from the CSR \rand.}
  \label{fig:etna}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale=0.355]{swarm.png}
  \label{fig:swarm}
  \caption{Histogram of individual-task speedups across different staging strategies and benchmarks. Extreme outliers correspond to large speedups.}
\end{figure}

@@

\section{Related Work}

\subsection{Speeding up Property-Based Testing}
\hg{\begin{itemize}
  \item Changing the generation order~\cite{runcimanSmallcheckLazySmallcheck2008,braquehaisSimpleIncrementalDevelopment2017}
  \item Dealing with filtering~\cite{claessenGeneratingConstrainedRandom2015}
  \item QuickerCheck~\cite{krookQuickerCheckImplementingEvaluating2024}
  \item Evaluation of PBT generation~\cite{shiEtnaEvaluationPlatform2023}
\end{itemize}}

\subsection{Staging Monadic Libraries}
\jwc{A generator is a parser of
randomness~\cite{goldsteinParsingRandomness2022}, and people have implemented
lots of staged parser libraries!}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib,harry}
